 

### 2021-09-01 vertical-thermal-review.Rmd
quick pass at big-picture SI needs
issue #53

#Appendices
appendix_NEON_methods <- "S1"
appendix_tealeaves_methods <- "S2"
appendix_lit_review_methods <- "S3"

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods for literature review"

@@

Appendix `r appendix_lit_review_methods`. `r appendix_lit_review_methods_title`

>>>>

#Appendices
appendix_NEON_methods <- "S1"
appendix_tealeaves_methods <- "S2"

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"

@@

### 2021-09-01 vertical-thermal-review_SI.Rmd
quick pass at big-picture SI needs
issue #53

#Appendices
appendix_NEON_methods <- "S1"
appendix_tealeaves_methods <- "S2"
appendix_lit_review_methods <- "S3"

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"
appendix_lit_review_methods_title<- "Methods for literature review"

#SI table numbers
SItable_example = "S1"

#SI table captions
SItable_example_legend <- "Table S1. ...."

@@

#SI figure captions
SIfig_example_legend <- "Figure S1. Vertical gradients in micrometeorological conditions for all forested sites in the National Ecological Observatory Network (NEON)"

@@

METHODS ON TEALEAVES GO HERE.

Energy balance for a normal overstory sun leaf and understory shade leaf were parameterized with biophysical variables from Harvard NEON data documented here: (https://github.com/EcoClimLab/vertical-thermal-review/blob/master/NEON_height_profiles/HARV_neon_stats.csv). Leaf trait measurements for leaf width, ie. measured as leaf characteristic dimmension, was measured on ~Quercus rubra~ sun and shade leaf, stomatal conductance measurements were referred from Tleaves typical sun and shade measurements [@muir_tealeaves_2019] and as well @cavender-baresChangesDroughtResponse2000.

@@

@@

#  Appendix `r appendix_lit_review_methods`. `r appendix_lit_review_methods_title`

METHODS ON LIT REVIEW GO HERE.

@@

# `r SIfig_example_legend`
![**Figure `r SIfig_NEON_all`. Vertical gradients in micrometeorological conditions for all forested sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in July mean ± 1 standard deviation for maximum photosyntehtically active ratiation (PAR), maximum wind speed, minimum humidity, maximum $T_{air}$, and maximum biological temperature, $T_{bio}$. Sites are grouped into the following categories: (A) (sub)subtropical and warm temperate broadleaf: ..., (B) temperate open/ savanna forests: ..., (C) temperate mesic broadleaf forests: ..., (D) temperate conifer forests: ..., (E) northern and boreal forests: ...  [Issue #35](https://github.com/EcoClimLab/vertical-thermal-review/issues/35). ](NEON_height_profiles/figures/profile_all_groups.png)

>>>>

# MAIN MANUSCRIPT DISPLAY ITEMS  (limit 8)
#figures
fig_schematic = 1
fig_NEON_vertical =  2
fig_leaf_T = 3
fig_treerings= 4 
fig_model=5

#tables
table_leaf_traits=1
table_leaf_metabolism=2

#Appendices
appendix_NEON_methods <- "S1"
appendix_tealeaves_methods <- "S2"

appendix_NEON_methods_title<- "Methods for NEON vertical profiles"
appendix_tealeaves_methods_title <- "Methods for leaf energy balance modeling"

#SI table numbers
Tealeaves_parameters = "S1"

#SI table captions
Tealeaves_parameters_legend <- "Table S1. Tealeaves parameters"

@@

#SI figure captions
SIfig_NEON_all_legend <- "Figure S1. Vertical gradients in micrometeorological conditions for all forested sites in the National Ecological Observatory Network (NEON)"

@@

Energy balance for a typical overstory sun leaf and understory shade leaf were modeled in the R package *Tleaves* [@muir_tealeaves_2019], parameterized for *Quercus rubra* L. leaves at Harvard Forest, MA, USA (**GEOGRAPHIC COORDINATES).
Parameters are presented in Table `r Tealeaves_parameters`.

*Describe where you came up with all the parameters:*

- micromet from NEON (explain exactly what you used)
- leaf characteristic dimension, was measured on *Quercus rubra* sun and shade leaf, 
- stomatal conductance measurements were referred from Tleaves typical sun and shade measurements [@muir_tealeaves_2019] 
- @cavender-baresChangesDroughtResponse2000.

@@

\newpage
# `r Tealeaves_parameters_legend `

Make a table from this:
https://github.com/EcoClimLab/vertical-thermal-review/blob/master/NEON_height_profiles/HARV_neon_stats.csv

@@

# `r SIfig_NEON_all_legend`
![**Figure `r SIfig_NEON_all`. Vertical gradients in micrometeorological conditions for all forested sites in the National Ecological Observatory Network (NEON)**. Shown are  height profiles in July mean ± 1 standard deviation for maximum photosyntehtically active ratiation (PAR), maximum wind speed, minimum humidity, maximum $T_{air}$, and maximum biological temperature, $T_{bio}$. Sites are grouped into the following categories: (A) (sub)subtropical and warm temperate broadleaf: ..., (B) temperate open/ savanna forests: ..., (C) temperate mesic broadleaf forests: ..., (D) temperate conifer forests: ..., (E) northern and boreal forests: ...  [Issue #35](https://github.com/EcoClimLab/vertical-thermal-review/issues/35). ](NEON_height_profiles/figures/profile_all_groups.png)

@@
